Modular Deep Encoder-Decoders

### 2016-04-28 paper/draft.tex
More on embedding, switched to RecurrentMean instead.

@@

@@

Paragraph: By using a standardized ds, we can fairly compare models...

@@

\subsection{Baseline}
\subsection{Proposed System}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{figs/multimodal.png}
\caption{Multi-modal Transfer Learning}
\end{figure}

@@

We tried two approaches when building the vector embedding from multiple modalities. The first one was to vertically stack the different embeddings from the different encoders and learn the actual embedding from a linear combination from this higher dimensional vector. This led to poor results and we instead decided to experiment with both the summing over every embedding, as well as taking their mean in each dimension.

@@

@@

TODO: Say if we ended up using RecurrentSum or RecurrentMean for the embedding. (see embedding layer section)
